\documentclass[12pt]{my_cv}
\usepackage[a4paper,left=1in,right=1in,top=1in,bottom=1in,footskip=0.25in]{geometry}
% https://www.overleaf.com/learn/latex/How_to_write_a_LaTeX_class_file_and_design_your_own_CV_(Part_1)#What_is_a_class_file?
\usepackage{helvet}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Raghav CV},
    pdfpagemode=FullScreen,
    }
\begin{document}
\begin{flushright}
\today
\end{flushright}

\textbf{{\Huge Raghav}} \hfill \url{https://raghav-bell.github.io}

209/2 Ward no.6, Vikas Nagar Gohana,

Haryana, India 131301

\textbf{Nationality:} Indian

\textbf{github} : \url{https://github.com/Raghav-Bell/}
\section{EDUCATION}
\begin{itemize}
\item \textbf{National Institute of Technology(NIT)} \hfill Kurukshetra, India
\\\textit{Bachelor of Technology (B.Tech), ECE} \hfill \textit{Jul, 2019 - Jun, 2023}
\end{itemize}
\section{EXPERIENCE}
\begin{itemize}
\item \textbf{Application Developer, IBM} \hfill \textit{Nov, 2023 - Current}
\\\textit{Safexpress Project.
\\Created Apex triggers, Flows, Batches etc as per business requirements.}
\item \textbf{Business Analyst, Udaan.com} \hfill \textit{Jan, 2022 - Jul, 2022}
\\\textit{Improvished retention analysing workflow.
\\Applied various statistical techniques like A-B testing, Bayesian statistics.}

\end{itemize}
\section{PROJECTS}
\begin{itemize}
\item \textbf{graby crate}
\\ \textit{A simple implementation of grep in rust and published on \href{https://crates.io/crates/graby}{crates.io}}
\item \textbf{Micro-ElectroMechanical Systems (MEMS) based piezoresistive pressure sensor}
\\\textit{A silicon diaphragm based piezoresistive pressure sensor.}
\item \textbf{Programmable Photonic Integrated Circuits}
\\\textit{Designed $8 \times 8$ MZI based triangular multiport interferometer.}
\item \textbf{NASA Space App Challenge 2022}
\\\textit{Analysed the seismic waves on moon data collected during NASA’s Apollo missions to classify various moonquakes.}
\item \textbf{Bolt meets Quantum}
\\\textit{Simulated Superdense Coding quantum protocol on Bolt Internet Of Things wi-fi module.}
\end{itemize}
\section{AWARDS}
\begin{itemize}
\item \textbf{Semi-Finalist at Hyundai Social Creator-2021} \hfill \textit{Mar, 2022}
\\\textit{One of the top 25 ideas among the 530 ideas submitted nationwide.}
\end{itemize}
\section{CERTIFICATIONS}
\begin{itemize}
\item \textbf{watsonx.data Technical Sales Intermediate} \hfill \textit{Mar, 2024}
\\ \textit{Issued by IBM}
\item \textbf{
Salesforce Certified AI Associate} \hfill \textit{Jan, 2024}
\\ \textit{Issued by Salesforce}
\item \textbf{Practical Introduction to Quantum-Safe Cryptography} \hfill \textit{Dec, 2023}
\\ \textit{Issued by IBM}
\item \textbf{Explorations into Mindfulness} \hfill \textit{Sep, 2023}
\\ \textit{Issued by IBM Skills Build}
\item \textbf{Qiskit Global Summer School 2023 - Quantum Excellence} \hfill \textit{Sep, 2023}
\\ \textit{Issued by IBM}
\item \textbf{Take your first steps with Rust} \hfill \textit{Aug, 2023}
\\ \textit{Issued by Microsoft}
\item \textbf{Deep Learning with Tensorflow} \hfill \textit{Jun, 2023}
\\ \textit{Issued by IBM Skills Build}
\item \textbf{IBM Garage Essential} \hfill \textit{Jun, 2023}
\\ \textit{Issued by IBM Skills Build}
\item \textbf{Options Trading Strategies In Python: Basic} \hfill \textit{Jun, 2023}
\\ \textit{Issued by QuantInsti \& NSE Academy }
\item \textbf{Penetration Testing and Ethical Hacking} \hfill \textit{Mar, 2023}
\\ \textit{Issued by Cybrary}
\item \textbf{Cybersecurity Fundamentals Badge} \hfill \textit{Mar, 2023}
\\ \textit{Issued by IBM Skills Build}
\item \textbf{Galactic Problem Solver} \hfill \textit{Oct, 2022}
\\ \textit{Issued by NASA Space APP Challenge}
\item \textbf{Qiskit Global Summer School 2022 - Quantum Excellence badge} \hfill \textit{Aug, 2022}
\\ \textit{Issued by IBM}
\item \textbf{Google IT Automation with Python} \hfill \textit{Jul, 2022}
\\ \textit{Issued by Coursera \& Google}
\item \textbf{VLSI SoC Design using Verilog HDL} \hfill \textit{Jun, 2022}
\\ \textit{Issued by Maven Silicon }
\item \textbf{Introduction to Fusion Energy and Plasma Physics}  \hfill \textit{Jun, 2022}
\\ \textit{Issued by Princeton Plasma Physics Laboratory Science Education Dept.}
\item \textbf{Google Data Analytics} \hfill \textit{Jun, 2022}
\\ \textit{Issued by Coursera \& Google}
\item \textbf{Internet of Things and Machine Learning} \hfill \textit{May, 2022}
\\ \textit{Issued by Bolt Iot}
\item \textbf{Goldman Sachs Engineering Virtual Program} \hfill \textit{Jul, 2021}
\\ \textit{Issued by Goldman Sachs} 
\item \textbf{Introduction to Quantum Computing Course } \hfill \textit{Oct, 2020 - May, 2021}
\\ \textit{Issued by The Coding School (Qubit by Qubit) \& IBM}
\item\textbf{ Geospatial applications for disaster risk management } \hfill \textit{Oct, 2020}
\\ \textit{Issued by ISRO, CSSTEAP \& UN-SPIDER}
\item \textbf{Python for Data Science badge}\hfill \textit{Aug, 2020}
\\ \textit{Issued by IBM P-TECH (now, IBM Skills Build)}
\item \textbf{Data Science Foundations - Level 1 badge}\hfill \textit{Jul, 2020}
\\ \textit{Issued by IBM P-TECH (now, IBM Skills Build)}

\end{itemize}
\section{HACKATHONS}
\begin{itemize}
\item \textbf{Hactoberfest, 2023} \hfill \textit{Oct, 2023}
\\ \textit{Organised by DigitalOcean}
\item \textbf{Symposium on Quantum Undergraduate Inquiry \& Discovery (SQUID)} \hfill \textit{Jun, 2023}
\\ \textit{Organised by group of students at Stanford University \& Yale university.}
\item \textbf{Massachusetts Institute of Technology iQuHACK} \hfill \textit{Jan, 2022}
\\ \textit{Organised by iQuISE, Massachusetts Institute of Technology.}
\item \textbf{Quantum Coalition Hackathon} \hfill \textit{Apr, 2021}
\\ \textit{Organised by group of students at Stanford University \& Yale university.}
\end{itemize}
\section{PRESENTATIONS}
\begin{itemize}
\item \textbf{Quantum Computing Seminar} \hfill \textit{Feb, 2023}
\\ \textit{Organised at NIT, Kurukshetra with Guncha Malik \& Ankur Raina}
\item \textbf{Bolt IOT meets Quantum} \hfill \textit{Jun, 2022}
\\ \textit{Organised on \href{https://youtu.be/iIxJa3kAFyI}{YouTube} with Bolt}
\end{itemize}
\section{KEY SKILLS}
\begin{itemize}
\item \textbf{Programming:} Python3, Bash, SQL, C, Verilog, Rust, Qiskit, \LaTeX, Apex, HTML, CSS, JS
\item \textbf{Software:} Jupyter notebooks, Iverilog, Git, Nano, Vim, Salesforce
\item \textbf{Hardware:} Arduino UNO,Bolt IOT wi-fi Module
\item \textbf{Technological Domains:} Quantum Computing, Machine Learning, Internet of Things, Penetration Testing, Integrated
Photonics
\end{itemize}
\section{REFERENCES}
\begin{itemize}
\item \textbf{Gourav Saini, gauravsaini@nitkkr.ac.in}
\\ \textit{Assistant Professor, Dept. of ECE, NIT Kurukshetra}
\item \textbf{Than Singh Saini, tss@nitkkr.ac.in}
\\ \textit{Assistant Professor, Dept. of Physics, NIT Kurukshetra}
\item \textbf{Yashashchandra Dwivedi, yashjidwivedi@nitkkr.ac.in}
\\ \textit{Assistant Professor, Dept. of Physics, NIT Kurukshetra}
\end{itemize}
\end{document}
