\documentclass[12pt]{my_cv}
\usepackage[a4paper,left=1cm,right=1cm,top=1cm,bottom=1cm,footskip=0.25cm]{geometry}
% https://www.overleaf.com/learn/latex/How_to_write_a_LaTeX_class_file_and_design_your_own_CV_(Part_1)#What_is_a_class_file?
\usepackage{helvet}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Raghav Resume},
    pdfpagemode=FullScreen,
    }
%\urlstyle{same}
\begin{document}
\begin{flushright}
\today
\end{flushright}
\begin{center}
\textbf{\Huge Raghav}

\href {mailto:raghavsingla327@gmail.com}{raghavsingla327@gmail.com} $|$ $+91$-$9518073978$ $|$ $209/2$ Ward no.$6$ Vikas Nagar Gohana Sonipat Haryana India $131301$ $|$
\href{https://linkedin.com/in/raghav-singla-78a926215/}{linkedin.com/in/raghav-singla-78a926215/} $|$  \href{https://raghav-bell.github.io}{raghav-bell.github.io}

\end{center}
\section{EXPERIENCE}
\begin{itemize}
\item \textbf{Application Developer, IBM} \hfill \textit{Nov, 2023 - Current}
\\\textit{Safexpress Project.
\\Created Apex triggers, Flows, Batches etc as per business requirements.}
\item \textbf{Business Analyst, Udaan.com} \hfill \textit{Jan, 2022 - Jul, 2022}
\\\textit{Improvished retention analysing workflow.
\\Applied various statistical techniques like A-B testing, Bayesian statistics.}

\end{itemize}
\section{PROJECTS}
\begin{itemize}
\item \textbf{graby crate}
\\ \textit{A simple implementation of grep in rust and published on \href{https://crates.io/crates/graby}{crates.io}}
\item \textbf{Micro-ElectroMechanical Systems (MEMS) based piezoresistive pressure sensor}
\\\textit{A silicon diaphragm based piezoresistive pressure sensor.}
\item \textbf{Programmable Photonic Integrated Circuits}
\\\textit{Designed $8 \times 8$ MZI based triangular multiport interferometer.}
\item \textbf{NASA Space App Challenge 2022}
\\\textit{Analysed the seismic waves on moon data collected during NASA’s Apollo missions to classify various moonquakes.}
\item \textbf{Bolt meets Quantum}
\\\textit{Simulated Superdense Coding quantum protocol on Bolt Internet Of Things wi-fi module.}
\end{itemize}
\section{AWARDS}
\begin{itemize}
\item \textbf{Semi-Finalist at Hyundai Social Creator-2021} \hfill \textit{Mar, 2022}
\\\textit{One of the top 25 ideas among the 530 ideas submitted nationwide.}
\end{itemize}
\section{EDUCATION}
\begin{itemize}
\item \textbf{National Institute of Technology(NIT) Kurukshetra, India} \hfill \textit{Jul, 2019 - Jun, 2023}
\\\textit{Bachelor of Technology (B.Tech), ECE}  \hfill CGPA: $7.9451$
\end{itemize}
\section{KEY SKILLS}
\begin{itemize}
\item \textbf{Programming:} Python3, Bash, SQL, C, Verilog, Rust, Qiskit, \LaTeX, Apex, HTML, CSS, JS. 
\textbf{Software:} Salesforce, Jupyter notebooks, Iverilog, Git, VsCode, Nano, Vim. 
\textbf{Hardware:} Arduino UNO,Bolt IOT wi-fi Module. 
\textbf{Technological Domains:} Quantum Computing, Machine Learning, Internet of Things, Penetration Testing, Integrated
Photonics.
\end{itemize}
\section{CERTIFICATIONS}
\begin{itemize}
\item \textbf{
Salesforce Certified AI Associate} \hfill \textit{Jan, 2024}
\\ \textit{Issued by Salesforce}
\item \textbf{Practical Introduction to Quantum-Safe Cryptography} \hfill \textit{Dec, 2023}
\\ \textit{Issued by IBM}
\item \textbf{Qiskit Global Summer School 2023 - Quantum Excellence} \hfill \textit{Sep, 2023}
\\ \textit{Issued by IBM}
\item \textbf{Take your first steps with Rust} \hfill \textit{Aug, 2023}
\\ \textit{Issued by Microsoft}
\item \textbf{Deep Learning with Tensorflow} \hfill \textit{Jun, 2023}
\\ \textit{Issued by IBM Skills Build}
\item \textbf{Penetration Testing and Ethical Hacking} \hfill \textit{Mar, 2023}
\\ \textit{Issued by Cybrary}
\item \textbf{Google IT Automation with Python} \hfill \textit{Jul, 2022}
\\ \textit{Issued by Coursera \& Google}
\item \textbf{Google Data Analytics} \hfill \textit{Jun, 2022}
\\ \textit{Issued by Coursera \& Google}
\item \textbf{VLSI SoC Design using Verilog HDL} \hfill \textit{Jun, 2022}
\\ \textit{Issued by Maven Silicon }
\end{itemize}
\end{document}